Empirical Evaluation of eval in R

### 2020-08-27 inst/analysis/analysis_stable.Rmd
Tags

eval_call_core <- 
  read_fst(core_filepath) %>%
  as_tibble() %>%
  mutate(dataset = "core")

eval_calls_raw <- bind_rows(eval_calls_packages, eval_call_core)
```

@@

r("default envir expr", nb_default_envir$n)
r("default envir expr percent", ratio(nb_default_envir$n, nb_eval_calls))
r("default envir  call sites percent", ratio(nb_call_sites_default_envir, nb_call_sites))
```

@@

classified_envir_prop_core %>%
  head(5) %>%
  add_column(index = toupper(letters)[1:5]) %>%
  pmap_dfr(function(env_class, n, proportion, index)
  {
    r(paste("core", "env class", index), env_class)
    r(paste("core", "count", index), n)
    r(paste("core", "proportion", index), percent(proportion))
  })

classified_envir_prop_packages %>%
  head(5) %>%
  add_column(index = toupper(letters)[1:5]) %>%
  pmap_dfr(function(env_class, n, proportion, index)
  {
    r(paste("packages", "env class", index), env_class)
    r(paste("packages", "count", index), n)
    r(paste("packages", "proportion", index), percent(proportion))
  })
```

>>>>

eval_calls_core <- 
  read_fst(core_filepath) %>%
  as_tibble() %>%
  mutate(dataset = "core")

eval_calls_raw <- bind_rows(eval_calls_packages, eval_calls_core)
```

@@

nb_default_envir_core <- count(default_envir %>% filter(dataset == "core"), wt = nb_ev_calls)

nb_eval_calls_core <- count(eval_calls_core, wt = nb_ev_calls)$n
nb_eval_calls_packages <- count(eval_calls_packages, wt = nb_ev_calls)$n

nb_default_envir_packages <- count(default_envir %>% filter(dataset == "packages"), wt = nb_ev_calls)

r("default envir expr", nb_default_envir$n)
r("default envir expr percent", ratio(nb_default_envir$n, nb_eval_calls))
r("default envir  call sites percent", ratio(nb_call_sites_default_envir, nb_call_sites))

r("default envir core expr percent", ratio(nb_default_envir_core$n, nb_eval_calls_core))
r("default envir packages expr percent", ratio(nb_default_envir_packages$n, nb_eval_calls_packages))
```

@@

nb_top_envir <- 8

classified_envir_prop_core %>%
  head(nb_top_envir) %>%
  add_column(index = toupper(letters)[1:nb_top_envir]) %>%
  pmap_dfr(function(env_class, n, proportion, index)
  {
    r(paste("core", "env class", index), env_class)
    r(paste("core", "count", index), n)
    r(paste("core", "proportion", index), percent(proportion))
  })

classified_envir_prop_packages %>%
  head(nb_top_envir) %>%
  add_column(index = toupper(letters)[1:nb_top_envir]) %>%
  pmap_dfr(function(env_class, n, proportion, index)
  {
    r(paste("packages", "env class", index), env_class)
    r(paste("packages", "count", index), n)
    r(paste("packages", "proportion", index), percent(proportion))
  })

envir_enclos <- classified_envir %>% filter(env_class %in% c("NULL", "list"))
nb_enclos <- count(envir_enclos, wt = nb_ev_calls)$n
r("nb enclos envir", nb_enclos)
r("enclos envir percent", ratio(nb_enclos, nb_eval_calls))

envir_sys_call <- classified_envir %>% filter(str_detect(env_class, fixed("sys.class")))
nb_sys_call <- count(envir_sys_call, wt = nb_ev_calls)$n
r("nb sys call envir", nb_sys_call)
r("sys call envir percent", ratio(nb_sys_call, nb_eval_calls))
```
